\textbf{Computational Fuzzy Extractors}

### 2013-05-17 CompFuzzExt.tex
messed with 4-4.2

Because we use a random linear code,  our decoding is limited to reconciling a logarithmic number of differences.  Unfortunately, we  cannot utilize the results that improve the decoding radius through the use of trapdoors (such as \cite{regev2005LWE}), because in a fuzzy extractor, there is no secret storage place for the trapdoor.

@@

We are able to relax the assumption that $w$ comes from the uniform distribution, and instead allow $w$ to come from a symbol-fixing source~\cite{KZ07} (each dimension is either uniform or fixed). This relaxation follows from new results about the hardness of LWE when samples have a fixed~(and adversarially known) error vector, which may be of independent interest~(\thref{thm:blockLWE}). See Section~\ref{}.

\paragraph{An Alternative Approach}  Computational extractors~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational} have the same goal of obtaining a pseudorandom key $r$ from a source $w$ in the setting without errors.  They can be constructed, for example, by applying to pseudorandom generator to the output of an information-theoretic extractor.  One way to build a computational \emph{fuzzy} extractor is by using a computational extractor instead  of the information-theoretic extractor in the construction of  \cite{DBLP:journals/siamcomp/DodisORS08}.   However, this approach is possible only if conditional min-entropy of $w$ conditioned on the sketch $s$ is high enough.  
%We ask whether it is possible to avoid this loss by making whole process ``computational.''
We compare the two approaches in \secref{sec:prg based comparison}.

@@

Intuitively, HILL entropy is as good as average min-entropy for all computationally-bounded observers.  Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.  
%Instead, in \secref{sec:unp secure sketch}, we relax the definition by allowing by outputting a new random variable that can be recovered when $\dis (w, w')\leq t$.  This object is the computational analogue of a fuzzy conductor~\cite{KanukurthiR09}.%This is a noisy computational conductor define computational secure sketches using unpredictability, and work with that definition for the rest of the paper.  
%  In \secref{sec:comp fuzzy extractors}, we show that computational fuzzy extractors can be constructed from  computational fuzzy conductors.
%The size of the circuits becomes important, we would like the \rec procedure to be computable by a circuit significantly smaller than the \hill entropy circuit size.  We simply include both of these parameters in the definition.  We review other definitions of computational entropy in Appendix~\ref{sec:notionsEntropy}.
We will consider secure sketches that retain relaxed HILL entropy: that is, we say that $(\sketch, \rec)$ is a  \emph{HILL-entropy~$(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon,s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\hillrlx}_{\epsilon, s_{sec}}(W|\sketch(W))\geq \tilde{m}$.

@@

We will say that a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-
hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\unp}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.  
Note this notion is quite natural: combining such a secure sketch via  \lemref{lem:fuzzy ext construction} with a particular type of extractor (called a extractor 
\emph{reconstructive}~\cite{barak-computational}), would yield a computational fuzzy extractor (per \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).

@@

In this section we describe our main construction.  In this section, we consider only a uniform source $W$; we consider other distributions in \secref{sec:LWE block fixing sources}.  Our construction uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.   Let $\decode_t$ be an algorithm that decodes a random linear code with at most $t$ errors (we will present such an algorithm later, in \label{sec:time main construction}).

\begin{construction}
Let $n$ be a security parameter and let $m> n$.  %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
Define $\gen, \rep$ as follows:%The following construction is a computational secure sketch:
%Code-offset construction of a secure sketch using a random linear code over a finite field $\Fq$. $\decode_t (\vA, \vect{D})$ denotes an algorithm that decodes up to $t$ errors, i.e., an algorithm that finds $X'\in \Fq^n$ such that $\vect{A}X'$ is of Hamming distance at most $t$ from $\vect{D}$. $m > n$ are parameters to be figured out later.
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w\leftarrow W$ (where $W$ is some distribution over $\Fq^m$).
\item Sample $\vA\in\Fq^{m\times n}, X\in\Fq^n$ uniformly.
\item Compute $p = (\vA, \vA X+w)$, \\\ $r = X_{1,...,n/2}$.
\item Output $(r, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rec}
\begin{enumerate}
\item \underline{Input}: $(w', p)$ (where the Hamming distance between $w'$ and $w$ is at most $t$).
\item Parse $p$ as $(\vA, \vect{C})$; let $\vect{D}=\vect{C}-w'$.
\item Let $X = \decode_t(\vA, \vect{D})$\\
\item Output $r = X_{1,...,n/2}$.
\end{enumerate}
\end{minipage} 
\end{tabular}
\end{center}
\label{cons:informal construction}
\end{construction}

Intuitively, security comes from the computational hardness of decoding random linear codes from a high number of errors (introduced by $w$).  
In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $\delta^{\mathcal{D}_{s_{sec}}}((X_{1,..., n/2},P), (U_{n/2 \log q}, P))\leq \epsilon$.  Furthermore, this construction is only useful if $\decode_t$ can be efficiently implemented.  We demonstrate an efficient $\decode_t$ that corrects a super-polynomial number of error patterns in polynomial time.

The rest of this section is devoted to making these intuitive statements precise.
 We describe the \class{LWE} problem and the security of our construction in \secref{subsec:LWE}.
 %a recent variant due to D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} in \secref{subsec:LWE}.  
We describe conditions for efficient decoding in \secref{sec:time main construction}.  In \secref{sec:lossless extractor}, we describe parameter settings where we extract as many bits as the size of our input distribution and thus our construction is lossless.  In \secref{sec:prg based comparison}, we compare \consref{cons:informal construction} to using a information-theoretic fuzzy extractor and running a pseudorandom generator on the output~(this is replacing the randomness extractor with a computational extractor).

\subsection{Security of \consref{cons:informal construction}}
\label{subsec:LWE}
The $\LWE$ problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise." For positive integers $n$ and $q \ge 2$, a vector $\vx \in \Fq^n$, and a probability distribution $\chi$ on $\Fq$, let $A_{\vect{x}, \chi}$ be the distribution obtained by choosing $\vA \overset{\$}\leftarrow \Fq^{m\times n}$ uniformly at random and a noise term $\ve \overset{\$}\leftarrow \chi^m$, and outputting $(\vA, \vA\vx+\ve)$. 
%The Learning With Errors ($\lwe$) is defined as follows: given access to the oracle that outputs a sample from the distribution $A_{\vx, \chi}$ for a uniform $\vx$, and output $\vx$ with high probability.

\begin{definition}[Decisional $\lwe$]\label{def:dist-LWE}Let $n$ be a security parameter.  
Let $m = m(n) = \poly(n)$ and $q = q(n) = \poly(n)$ be integers. The decisional version of the $\LWE$ problem, denoted \class{dist}-$\LWE_{n, m, q, \chi}$, is to distinguish between $m$ samples chosen according to $A_{\vx, \chi}$ for a uniformly random $\vx$ from samples chosen according to the uniform distribution over $(\Fq^{m\times n}, \Fq^m)$.

We say that $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})$-secure if no (probabilistic) distinguisher of size $s_{sec}$ can distinguish the $\lwe$ instances from uniform except with probability $\epsilon$.  If $\distLWE_{n, m, q, \chi}$ is secure for all $s_{sec} = \poly(n), \epsilon  = 1/\poly(n)$ we say it is \emph{secure}.
\end{definition}

Denote by $\bar{\Psi}_\alpha$ the discretized Gaussian distribution over $\Fq$ with variance $(\alpha q)^2/(2\pi)$, Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that, when $\chi = \bar{\Psi}_{\alpha}$, $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure if the worst-case lattice problems are hard to approximate using quantum algorithms.
%The matrix $\vA$ and secret $\vx$ are drawn from the uniform distribution, while the error term is drawn from a discretized Gaussian distribution $\bar{\Psi}_{\alpha}$.  
Furthermore, Regev \cite{regev2005LWE} shows a decision to search equivalence for $q=\poly(n)$.
%We state the decisional version in terms of unpredictability entropy~(see \defref{def:unp entropy} for the definition of unpredictability entropy and \secref{sec:LWEoverview} for an equivalence to the standard formulation of decisional LWE):

@@

We cannot immediately adapt the construction in \consref{cons:informal construction} to the $\LWE$ problem.  Standard formulations of $\LWE$ require the error term to come from the discretized Gaussian distribution.  
%\subsection{LWE with uniform errors}
%\label{subsec:LWE uniform error}
Recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$ with the uniform distribution over a small interval reduces to the security of $\LWE$ where the noise comes from the discretized Gaussian\footnote{Micciancio and Peikert provide a similar formulation in~\cite{micciancio2013hardness}.  The result D\"{o}ttling and M\"{u}ller-Quade provides better parameters for our setting.}.  This allows us to directly encode $w$ as the error term in an $\LWE$ problem by splitting it  into $m$ blocks.  The size of these blocks is dictated by the following result of D\"{o}ttling and M\"{u}ller-Quade:
%As stated above this has two advantages for Construction~\ref{cons:LWESecureSketch}: 1) the bits of $W$ can be used directly and \rep can output $w$ instead of $sam_w$ 2) there is a fixed number of bits required to sample each dimension.  
%We present the formulation of D\"{o}ttling and M\"{u}ller-Quade: 
%\begin{lemma}~\protect{~\cite[Theorem 5]{dottling2012}}
%\label{lem:uniform LWE}
%Let $n$ be a security parameter.  Let $q = q(n))$ and $m = m(n) = \poly(n)$ be integers.  Let $\rho = \rho(n) \in (0,1)$ be such that $\rho q\geq 2n^2m$.  Assume there exists a PPT-algorithm that solves the LWE decision problem where $\vA,X$ are drawn uniformly at random and $E$ is drawn from the interval $[-\rho q, \rho q]$ with non-negligible probability.  Then there exists an efficient quantum-algorithm that approximates the decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) to within $\tilde{O}(n^{5/2}m/\rho)$ in the worst case.
%\end{lemma}

@@

\subsection{Efficiency of \consref{cons:informal construction}}
\label{sec:time main construction}
%\subsection{Analysis of Construction~\ref{cons:LWESecureSketch}}
\consref{cons:informal construction} is only useful if $\decode_t$ can be efficiently implemented.  We now present a particular $\decode_t$ and consider its efficiency:

\begin{construction}
\label{cons:decoding algorithm} We consider a setting of $(n, m, q, \chi)$ where $m\geq 3n$.  We describe $\decode_t$:
\begin{enumerate}
\item Input $\vA , B = \vA X + W - W'$
\item Randomly select rows without replacement $i_1,..., i_{2n}\leftarrow [1,m]$.  
\item Restrict $\vA, B$ to rows $i_1,...,i_{2n}$, denote this as $\vA_{i_1,...,i_{2n}}, B_{i_1,...,i_{2n}}$.
\item Find $n$ rows of $\vA_{i_1,..., i_{2n}}$ that are linearly independent.  
Denote by $\vA', B'$ the restriction of $\vA_{i_1,..., i_{2n}}, B_{i_1,..., i_{2n}}$ (respectively) to these rows.  If no such rows exist go to step (2).
\item Compute $X' = (\vA')^{-1}B'$.  If $B- AX'$ has more than $t$ nonzero coordinates, go to step (2).
\item Output $X'$.
\end{enumerate}
\end{construction}

$\decode_t$ is an efficient decoding procedure when $t$ is small enough.  We need $t$ to be small enough for none of the selected rows to have errors with probability at least $\frac{1}{\poly(n)}$, furthermore, we need the code generated by $\vA$ to have distance at least $t$ with high probability.  The second condition is to ensure that there are few false positives in step (5).  This condition is satisfied for $t = O(\frac{m}{n}\log n)$, since random codes have high distance with probability $1-e^{-\Omega(n)}$.  The exact statement is in \corref{cor:code high distance}.  Furthermore, steps (3-5) are computable in time $O(n^3)$.
This is also a sufficient condition for steps (3-5) to succeed with probability at least $1/\poly(n)$.  We consider the setting where the running time of $\decode_t$ grows with $t$.  $\decode_t$ is efficient as long as $t$ is small enough.  The formal statement is below~(proof in \secref{sec:proof lem i t poly time}):
%  We provide the results in \lemref{lem:i t constant time} and \lemref{lem:i t poly time} respectively~(proofs in Sections~\ref{sec:proof lem i t constant time},~\ref{sec:proof lem i t poly time}).  \lnote{can we combine these lemmas into one?  It's hard for the reader to compare line-by-line to see where the differences are.  More errors seems better; we could simply point out that constant number of erros leads to better running time, right in the statement of the lemma or right after it}
%\begin{lemma}[Efficiency of $\decode_t$ when $t\leq m/n-1$]
%\label{lem:i t constant time}
%Let $\vA, \vA X+E$ be a  $(n,m, q, \chi)$-LWE instance that is a unique witness relation~(except with negligible probability).  Assume $d(E, E')\leq t$ where $t \leq (m-n)/n$.  Then $\decode_t$ runs in expected time $O(n^3\log q+ s_{ver})$ on input distribution $\vA, \vA X+E - E'$ and outputs $X' =X$ for all but a negligible fraction of inputs over $\vA, \vA X+E - E'$.
%\end{lemma}
\begin{lemma}[Efficiency of $\decode_t$ when $t\leq d\log n (m/n-2)$]
\label{lem:i t poly time}
Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance where $m\geq 3n$.  Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$.  Let $d$ be a constant and assume that $\dis(W, W')\leq t$ where $t\leq d\log n(\frac{m}{n}-2)$.  Then $\decode_t$ runs in expected time $O(n^{4d}(n^3\log q))$ on input distribution $\vA, \vA X+W - W'$ and outputs $W$ with probability $1-e^{-\Omega(n)}$ when $\vA$ is a random matrix.
\end{lemma}
\textbf{Note:} If we consider the setting where $t\leq m/n-2$, then $\decode_t$ will run in expected time $O(n^3\log n)$.  Our main theorems apply when $t\leq m/n-2$ with slightly better parameters.  We concentrate on the setting $t\leq d\log n(m/n-2)$.  Also even though we are correcting $O(\log n)$ errors, this a super polynomial number of error patterns and the running time of $\decode_t$ is significantly better than exhaustive search over these error patterns.

@@

Thus, using the same assumptions as \thref{thm:lossless secure conductor log}, we can obtain a computational extractor.  This means we could  build a computational fuzzy extractor using: 1) an information-theoretic secure sketch 2) a computational extractor.
We call the paradigm of running a secure sketch and using a computational extractor \emph{sketch-then-cextract}.

Any improvement in computational extractors yields an improvement to the \emph{sketch-then-cextract} construction of a computational fuzzy extractor.  Similarly, a computational fuzzy extractor is also a computational extractor~(ignoring the \rep functionality).  Thus, improving computational fuzzy extractors may improvement computational extractors.

The main advantage to analyzing the construction as a whole~(instead of \emph{sketch-then-cextract}) is that security need not depend on the decoding radius $t$.  In \emph{sketch-then-cextract} paradigm, the computational extractor must be able to handle sources with $\Hoo(W| \sketch(W))$.  As shown in \secref{sec:defCompFuzzyExtractors}, this value depends on bounds from error-correcting codes.  In our construction, the decoding radius does not affect the security of the construction.  The decoding radius only impacts the running time of the decoding algorithm.  Conceivably, a computational fuzzy extractor could be built where only correctness depends on $t$~(not efficiency or security).
%However, the construction of a computational fuzzy extractor by 
%The advantage of \consref{cons:informal construction} is that losses due to error correction $O(\log |B_t(\cdot)|)$ and randomness extraction $O(\log 1/\epsilon)$ are not necessary.  In the case where $W$ is small, these losses may leave too few bits for a secure pseudorandom generator.  The work of~\cite{dachman2012computational} shows that these losses in the extract-then-expand construction are in some sense necessary~(the samplable RT conjecture in~\cite{dachman2012computational} has been resolved positively by~\cite{dodis2013key}).

>>>>

Because we use a random linear code,  our decoding is limited to reconciling a logarithmic number of differences.  Unfortunately, we  cannot utilize the results that improve the decoding radius through the use of trapdoors (such as \cite{regev2005LWE}), because in a fuzzy extractor, there is no secret storage place for the trapdoor. If improved decoding algorithms are obtained for random linear codes, they will improve error-tolerance of our construction.

@@

In \secref{sec:LWE block fixing sources}, we are able to relax the assumption that $w$ comes from the uniform distribution, and instead allow $w$ to come from a symbol-fixing source~\cite{KZ07} (each dimension is either uniform or fixed). This relaxation follows from our results about the hardness of LWE when samples have a fixed~(and adversarially known) error vector, which may be of independent interest~(\thref{thm:blockLWE}).

\paragraph{An Alternative Approach}  Computational extractors~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational} have the same goal of obtaining a pseudorandom key $r$ from a source $w$ in the setting without errors.  They can be constructed, for example, by applying to pseudorandom generator to the output of an information-theoretic extractor.  One way to build a computational \emph{fuzzy} extractor is by using a computational extractor instead  of the information-theoretic extractor in the sketch-and-extract construction of  \cite{DBLP:journals/siamcomp/DodisORS08}.   However, this approach is possible only if conditional min-entropy of $w$ conditioned on the sketch $s$ is high enough.  
%We ask whether it is possible to avoid this loss by making whole process ``computational.''
We compare the two approaches in \secref{sec:prg based comparison}.

@@

Intuitively, HILL entropy is as good as average min-entropy for all computationally-bounded observers.  Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the sketch-and-extract construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.  
%Instead, in \secref{sec:unp secure sketch}, we relax the definition by allowing by outputting a new random variable that can be recovered when $\dis (w, w')\leq t$.  This object is the computational analogue of a fuzzy conductor~\cite{KanukurthiR09}.%This is a noisy computational conductor define computational secure sketches using unpredictability, and work with that definition for the rest of the paper.  
%  In \secref{sec:comp fuzzy extractors}, we show that computational fuzzy extractors can be constructed from  computational fuzzy conductors.
%The size of the circuits becomes important, we would like the \rec procedure to be computable by a circuit significantly smaller than the \hill entropy circuit size.  We simply include both of these parameters in the definition.  We review other definitions of computational entropy in Appendix~\ref{sec:notionsEntropy}.
We will consider secure sketches that retain relaxed HILL entropy: that is, we say that $(\sketch, \rec)$ is a  \emph{HILL-entropy~$(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon,s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\hillrlx}_{\epsilon, s_{sec}}(W|\sketch(W))\geq \tilde{m}$.

@@

We will say that a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-
hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\unp}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.  
Note this notion is quite natural: combining such a secure sketch in a sketch-and-extract construction of  \lemref{lem:fuzzy ext construction} with a particular type of extractor (called a extractor 
\emph{reconstructive}~\cite{barak-computational}), would yield a computational fuzzy extractor (per \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).

@@

In this section we describe our main construction.  In this section, we consider only a uniform source $W$; we consider other distributions in \secref{sec:LWE block fixing sources}.  Our construction uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.   Let $\decode_t$ be an algorithm that decodes a random linear code with at most $t$ errors (we will present such an algorithm later, in \secref{sec:time main construction}).

\begin{construction}
Let $n$ be a security parameter and let $m> n$.  Let $q$ be a prime. %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
Define $\gen, \rep$ as follows:%The following construction is a computational secure sketch:
%Code-offset construction of a secure sketch using a random linear code over a finite field $\Fq$. $\decode_t (\vA, \vect{D})$ denotes an algorithm that decodes up to $t$ errors, i.e., an algorithm that finds $X'\in \Fq^n$ such that $\vect{A}X'$ is of Hamming distance at most $t$ from $\vect{D}$. $m > n$ are parameters to be figured out later.
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w\leftarrow W$ (where $W$ is some distribution over $\Fq^m$).
\item Sample $\vA\in\Fq^{m\times n}, X\in\Fq^n$ uniformly.
\item Compute $p = (\vA, \vA X+w)$, \\\ $r = X_{1,...,n/2}$.
\item Output $(r, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rec}
\begin{enumerate}
\item \underline{Input}: $(w', p)$ (where the Hamming distance between $w'$ and $w$ is at most $t$).
\item Parse $p$ as $(\vA, \vect{C})$; let $\vect{D}=\vect{C}-w'$.
\item Let $X = \decode_t(\vA, \vect{D})$\\
\item Output $r = X_{1,...,n/2}$.
\end{enumerate}
\end{minipage} 
\end{tabular}
\end{center}
\label{cons:informal construction}
\end{construction}

Intuitively, security comes from the computational hardness of decoding random linear codes from a high number of errors (introduced by $w$).  
In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $\delta^{\mathcal{D}_{s_{sec}}}((X_{1,..., n/2},P), (U_{n/2 \log q}, P))\leq \epsilon$.  Furthermore, this construction is only useful if $\decode_t$ can be efficiently implemented.

The rest of this section is devoted to making these intuitive statements precise.
 We describe the \class{LWE} problem and the security of our construction in \secref{subsec:LWE}.
 %a recent variant due to D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} in \secref{subsec:LWE}.  
We describe one possible polynomial-time $\decode_t$ (which corrects more errors than is possible by exhaustive search) in \secref{sec:time main construction}.  In \secref{sec:lossless extractor}, we describe parameter settings where we extract as many bits as the size of our input distribution and thus our construction is lossless.  In \secref{sec:prg based comparison}, we compare \consref{cons:informal construction} to using a sketch-and-extract approach (\lemref{lem:fuzzy ext construction}) instantiated with a computational extractor.

\subsection{Security of \consref{cons:informal construction}}
\label{subsec:LWE}
The $\LWE$ problem was introduced by Regev \cite{regev2005LWE, regevLWEsurvey} as a generalization of ``learning parity with noise." For a positive integers $n$,  a prime $q$, a vector $\vx \in \Fq^n$, and a probability distribution $\chi$ on $\Fq$, let $A_{\vect{x}, \chi}$ be the distribution obtained by choosing $\vA \overset{\$}\leftarrow \Fq^{m\times n}$ uniformly at random and a noise term $\ve \overset{\$}\leftarrow \chi^m$, and outputting $(\vA, \vA\vx+\ve)$. 
%The Learning With Errors ($\lwe$) is defined as follows: given access to the oracle that outputs a sample from the distribution $A_{\vx, \chi}$ for a uniform $\vx$, and output $\vx$ with high probability.

\begin{definition}[Decisional $\lwe$]\label{def:dist-LWE}Let $n$ be a security parameter.  
Let $m = m(n) = \poly(n)$ be an integer $q = q(n) = \poly(n)$ be a prime. The decisional version of the $\LWE$ problem, denoted \class{dist}-$\LWE_{n, m, q, \chi}$, is to distinguish between $m$ samples chosen according to $A_{\vx, \chi}$ for a uniformly random $\vx$ from samples chosen according to the uniform distribution over $(\Fq^{m\times n}, \Fq^m)$.

We say that $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})$-secure if no (probabilistic) distinguisher of size $s_{sec}$ can distinguish the $\lwe$ instances from uniform except with probability $\epsilon$.  If $\distLWE_{n, m, q, \chi}$ is secure for all $s_{sec} = \poly(n), \epsilon  = 1/\poly(n)$, we say it is \emph{secure}.
\end{definition}

Denote by $\bar{\Psi}_\alpha$ the discretized Gaussian distribution over $\Fq$ with variance $(\alpha q)^2/(2\pi)$. Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that, when $\chi = \bar{\Psi}_{\alpha}$, $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure if the worst-case lattice problems are hard to approximate using quantum algorithms.
%The matrix $\vA$ and secret $\vx$ are drawn from the uniform distribution, while the error term is drawn from a discretized Gaussian distribution $\bar{\Psi}_{\alpha}$.  
Furthermore, Regev \cite{regev2005LWE} shows a decision to search equivalence for $q=\poly(n)$.
%We state the decisional version in terms of unpredictability entropy~(see \defref{def:unp entropy} for the definition of unpredictability entropy and \secref{sec:LWEoverview} for an equivalence to the standard formulation of decisional LWE):

@@

The above formulation of $\LWE$ requires the error term to come from the discretized Gaussian distribution, which makes it difficult to use it for constructing fuzzy extractors (because using $w$ and $w'$ to sample Gaussian distributions will increase the distance between the error terms and/or reduce their entropy).
%\subsection{LWE with uniform errors}
%\label{subsec:LWE uniform error}
Fortunately, recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$ when errors come from the uniform distribution over a small interval (assuming the security of $\LWE$ when errors come from the discretized Gaussian\footnote{Micciancio and Peikert provide a similar formulation in~\cite{micciancio2013hardness}.  The result D\"{o}ttling and M\"{u}ller-Quade provides better parameters for our setting.}.  This allows us to directly encode $w$ as the error term in an $\LWE$ problem by splitting it  into $m$ blocks.  The size of these blocks is dictated by the following result of D\"{o}ttling and M\"{u}ller-Quade:
%As stated above this has two advantages for Construction~\ref{cons:LWESecureSketch}: 1) the bits of $W$ can be used directly and \rep can output $w$ instead of $sam_w$ 2) there is a fixed number of bits required to sample each dimension.  
%We present the formulation of D\"{o}ttling and M\"{u}ller-Quade: 
%\begin{lemma}~\protect{~\cite[Theorem 5]{dottling2012}}
%\label{lem:uniform LWE}
%Let $n$ be a security parameter.  Let $q = q(n))$ and $m = m(n) = \poly(n)$ be integers.  Let $\rho = \rho(n) \in (0,1)$ be such that $\rho q\geq 2n^2m$.  Assume there exists a PPT-algorithm that solves the LWE decision problem where $\vA,X$ are drawn uniformly at random and $E$ is drawn from the interval $[-\rho q, \rho q]$ with non-negligible probability.  Then there exists an efficient quantum-algorithm that approximates the decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) to within $\tilde{O}(n^{5/2}m/\rho)$ in the worst case.
%\end{lemma}

@@

\subsection{Efficiency of \consref{cons:informal construction}}
\label{sec:time main construction}
%\subsection{Analysis of Construction~\ref{cons:LWESecureSketch}}
\consref{cons:informal construction} is only useful if $\decode_t$ can be efficiently implemented.  We need a decoding algorithm for a random linear code with $t$ errors that runs in polynomial time.  We present a simple $\decode_t$.  Replacing our algorithm  with a state of the art algorithm will only increase our correcting capability and improve \consref{cons:informal construction}.

\begin{construction}
\label{cons:decoding algorithm} We consider a setting of $(n, m, q, \chi)$ where $m\geq 3n$.  We describe $\decode_t$:
\begin{enumerate}
\item Input $\vA , B = \vA X + W - W'$
\item Randomly select rows without replacement $i_1,..., i_{2n}\leftarrow [1,m]$.  
\item Restrict $\vA, B$ to rows $i_1,...,i_{2n}$, denote this as $\vA_{i_1,...,i_{2n}}, B_{i_1,...,i_{2n}}$.
\item Find $n$ rows of $\vA_{i_1,..., i_{2n}}$ that are linearly independent.  
If no such rows exist go to step (2).
\item Denote by $\vA', B'$ the restriction of $\vA_{i_1,..., i_{2n}}, B_{i_1,..., i_{2n}}$ (respectively) to these rows. Compute $X' = (\vA')^{-1}B'$.  If $B- AX'$ has more than $t$ nonzero coordinates, go to step (2).
\item Output $X'$.
\end{enumerate}
\end{construction}

$\decode_t$ is an efficient decoding procedure when $t$ is small enough.  We need $t$ to be small enough for none of the selected rows to have errors with probability at least $\frac{1}{\poly(n)}$. Furthermore, we need the code generated by $\vA$ to have distance at least $t$ with high probability.  The second condition is to ensure that there are few false positives in step (5).  This condition is satisfied for $t = O(\frac{m}{n}\log n)$, since random codes have high distance with probability $1-e^{-\Omega(n)}$.  The exact statement is in \corref{cor:code high distance}.  Furthermore, steps (3-5) are computable in time $O(n^3)$.
This is also a sufficient condition for steps (3-5) to succeed with probability at least $1/\poly(n)$.  We consider the setting where the running time of $\decode_t$ grows with $t$.  $\decode_t$ is efficient as long as $t$ is small enough.  The formal statement is below~(proof in \secref{sec:proof lem i t poly time}):
%  We provide the results in \lemref{lem:i t constant time} and \lemref{lem:i t poly time} respectively~(proofs in Sections~\ref{sec:proof lem i t constant time},~\ref{sec:proof lem i t poly time}).  \lnote{can we combine these lemmas into one?  It's hard for the reader to compare line-by-line to see where the differences are.  More errors seems better; we could simply point out that constant number of erros leads to better running time, right in the statement of the lemma or right after it}
%\begin{lemma}[Efficiency of $\decode_t$ when $t\leq m/n-1$]
%\label{lem:i t constant time}
%Let $\vA, \vA X+E$ be a  $(n,m, q, \chi)$-LWE instance that is a unique witness relation~(except with negligible probability).  Assume $d(E, E')\leq t$ where $t \leq (m-n)/n$.  Then $\decode_t$ runs in expected time $O(n^3\log q+ s_{ver})$ on input distribution $\vA, \vA X+E - E'$ and outputs $X' =X$ for all but a negligible fraction of inputs over $\vA, \vA X+E - E'$.
%\end{lemma}
\begin{lemma}[Efficiency of $\decode_t$ when $t\leq d\log n (m/n-2)$]
\label{lem:i t poly time}
Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance where $m\geq 3n$.  Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$.  Let $d$ be a constant and assume that $\dis(W, W')\leq t$ where $t\leq d\log n(\frac{m}{n}-2)$.  Then $\decode_t$ runs in expected time $O(n^{4d}(n^3\log q))$ on input distribution $\vA, \vA X+W - W'$ and outputs $W$ with probability $1-e^{-\Omega(n)}$ when $\vA$ is a random matrix.
\end{lemma}
\textbf{Note:} If we consider the setting where $t\leq m/n-2$, then $\decode_t$ will run in expected time $O(n^3\log n)$.  Our main theorems apply when $t\leq m/n-2$ with slightly better parameters.  We concentrate on the setting $t\leq d\log n(m/n-2)$.  Also even though we are correcting $O(\log n)$ errors, this a super polynomial number of error patterns and the running time of $\decode_t$ is significantly better than exhaustive search over these error patterns.

@@

Thus, using the same assumptions as \thref{thm:lossless secure conductor log}, we can obtain a computational extractor.  This means we could  build a computational fuzzy extractor using: 1) an information-theoretic secure sketch 2) a computational extractor.
We call the paradigm of running a secure sketch and using a computational extractor \emph{sketch-and-comp-extract}.

Any improvement in computational extractors yields an improvement to the sketch-and-comp-extract construction of a computational fuzzy extractor.  Similarly, a computational fuzzy extractor is also a computational extractor~(ignoring the \rep functionality).  Thus, improving computational fuzzy extractors may improvement computational extractors.

The main advantage to analyzing the construction as a whole~(instead of sketch-and-comp-extract) is that security need not depend on the decoding radius $t$.  In sketch-and-comp-extract paradigm, the computational extractor must be able to handle sources with $\Hoo(W| \sketch(W))$.  As shown in \secref{sec:impossCompSecSketch}, this value depends on bounds from error-correcting codes.  In our construction, the decoding radius does not affect the security of the construction.  The decoding radius only impacts the running time of the decoding algorithm.  Conceivably, a computational fuzzy extractor could be built where only correctness depends on $t$~(not efficiency or security).
%However, the construction of a computational fuzzy extractor by 
%The advantage of \consref{cons:informal construction} is that losses due to error correction $O(\log |B_t(\cdot)|)$ and randomness extraction $O(\log 1/\epsilon)$ are not necessary.  In the case where $W$ is small, these losses may leave too few bits for a secure pseudorandom generator.  The work of~\cite{dachman2012computational} shows that these losses in the extract-then-expand construction are in some sense necessary~(the samplable RT conjecture in~\cite{dachman2012computational} has been resolved positively by~\cite{dodis2013key}).
